\documentclass{article}
\usepackage[left=2.5cm,right=2.5cm,top=2cm,bottom=3cm]{geometry}

\include{proposal.preamble}

\begin{document}
\title{NeuroSpectator: Real-time Cognitive
Insights with Brain and Physiological data
in Competitive Multiplayer Gaming}
\author{Benjamin Adonis}
\studentid{20371708}
\email{psyba3@nottingham.ac.uk}
\supervisor{Horia Maior}
\modulecode{COMP4029}
\date{October 2024}

\maketitle

\section{Background and Motivation}


\section{Aims and Objectives}
Aim: To develop a secure cloud based streaming platform that allows online competitive players to broadcast their gameplay and associated brain and psychological data to spectators and for gameplay review, using the platform’s client, BCI and consumer grade BCI devices.\par
Key Objectives:
\begin{enumerate}
    \item Research must be conducted to understand the user requirements of online competitive players and spectators
    \item Research must be conducted into the value of each of the brain and psychological data analytics that can be obtained from a consumer grade BCI device
    \item This data must be useful such that spectators can interpret the information to benefit their understanding of the players mental state and how it affects their gameplay
    \item The streaming platform must maintain data privacy measures and adhere to ethical guidelines
    \item Brain data visualisations must be meaningful, shown in real-time and associated with in game events 
    \item The streaming platform must be structured such that mods for supported online competitive games can be installed to allow for a BCI device to be used.
    \item User studies must be conducted with prototyping to assess the significance, convenience and viability of the streaming platform and BCI and BCI Device usage.

\end{enumerate}
\end{enumerate}

\section{External Aspect}
This project covers multiple fields in brain data research and online entertainment and the competitive eSports scene. Within the University of Nottingham Brain and Psychological Data Group research is ongoing into the usage of fNIRS,  mixed reality, HCI and adoption of consumer neurotechnology. In online spaces such as Twitch, BCIs have been utilised for challenge runs of games for entertainment purposes. The eSports scene is growing in significance where recently the International Olympics Committee has created the Olympic eSports Games. By adopting a consumer level entry to this project, the outcome should be a product that had research interest and real world application for a broad demographic.

\section{Work Plan}


\bibliography{docs/preliminary/bibliography/bibliography}
\end{document}